Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-07 STAT-paper-template/APA/fertile.Rnw
added tibble list of checks

@@

Subsets of the sixteen tests can be invoked using the \pkg{tidyselect} helper functions \citep{R-tidyselect} in combination with the more limited \func{proj\_check\_some} function. \textcolor{blue}{These helper functions, which include \func{starts\_with}, \func{ends\_with}, \func{contains}, and \func{matches}, allow users to check for matches between a string or regular expression and a list of variables--in this case, searching for checks from the list in \func{list\_checks} whose names match a certain condition (i.e. ending with "root")}.

>>>>

<<list of checks, echo = FALSE>>=
check_name <- c("has_proj_root()",
           "has_no_nested_proj_root()",
           "has_clear_build_chain()",
           "has_tidy_[media/images/code/raw_data/data/scripts]()",
           "has_only_used_files()",
           "has_readme()",
           "has_well_commented_code()",
           "has_no_absolute_paths()",
           "has_only_portable_paths()",
           "has_no_randomness()",
           "has_no_lint()")

description <- c(
  "Checks to make sure a single .Rproj file is found in the root directory of the project.",
  "Checks to make sure there are no nested .Rproj files in subfolders of the project.",
  "Looks for indication of a clear order in which to run R scripts.",
  "There are six different ”has_tidy_...” functions. Each checks to make sure that no files of its given type (images, code, data, etc.) are located in the root directory of the project",
  "Ensures that all files located in the project directory are being referenced or created by other files in the project.",
  "Checks to make sure there is a README file in the root directory.",
  "Checks to ensure that all code files contain an adequate number of comments (>10% of lines).",
  "Checks to make sure that no absolute paths are referenced in code.",
  "Checks to make sure that no paths in code lead outside the project directory.",
  "Checks to make sure code does not contain uncontrolled randomness.",
  "Examines code to determine whether it conforms to ”tidy” style guide recommendations.")

checks_list <- tidyr::tibble(check_name, description)
@

@@

Subsets of the sixteen tests can be invoked using the \pkg{tidyselect} helper functions \citep{R-tidyselect} in combination with the more limited \func{proj\_check\_some} function. \textcolor{blue}{These helper functions, which include \func{starts\_with}, \func{ends\_with}, \func{contains}, and \func{matches}, allow users to check for matches between a string or regular expression and a list of variables--in this case, searching for checks from the list provided by \func{list\_checks} whose names match a certain condition (i.e. ending with "root")}.

### 2020-10-07 STAT-paper-template/APA/fertile.tex
added tibble list of checks

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-07 17:58:10
## 2 package:for~ <NA>                                 base::l~ 2020-10-07 17:58:10
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-07 17:58:10
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file)
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7f81bb25c1d8>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpKbQKHU/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpKbQKHU/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpKbQKHU/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpKbQKHU/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-07 18:10:27
## 2 package:for~ <NA>                                 base::l~ 2020-10-07 18:10:27
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-07 18:10:27
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file)
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7f98482ffa60>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxVNb0M/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxVNb0M/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxVNb0M/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpxVNb0M/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}
